The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-04-10 paper.tex
Ready for submission

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal-to-noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
Most of the galaxies for the KMOS observations had a confirmed spectroscopic redshift (see below).
A subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
In each pointing, few sources had no spectroscopic redshift and were selected on the basis of their photometric redshift.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).

@@

Two of the three field environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We selected targets from the various spectroscopic campaigns which have targeted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
We name these GOODS-S-P1 and GOODS-S-P2, which which we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies quoted for GOODS-S-P2 does not include two observed targets which were later found to have $z < 0.5$.}

@@

To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however, due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

\subsubsection{Applying {\tt GALFIT} to the imaging data}\label{subsubsec:galfitting}
We used {\tt GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
The GOODS-S imaging data used is the latest release of the total field in {\it WFC3 F160W} band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
For SSA22 we made use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the {\it WFC3 F160W} band (P.I. Lehmer: PID 13844; P.I. Mannucci: PID 11735) and the {\it ACS F814W} band, tracing $\simeq$ 2500$\AA$ light at $z\simeq3.1$ (P.I. Chapman: PID 10405; P.I. Abraham: PID 9760; P.I. Siana: PID 12527).
The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the {\it F160W} coverage is concentrated on the SSA22-cluster and so we resorted to the bluer {\it ACS F814W} data to derive morphological parameters in SSA22-P2 (also in SSA22-P2, 4 galaxies do not have any {\em HST} coverage as indicated in Table \ref{tab:phys-props}). \\

\noindent
We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
In the {\it F160W} band, the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.

@@

\noindent
This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
Example {\em HST} images and {\tt GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.

The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
In each of the following sections we also discuss the approach followed to recover the morphological parameters for the galaxies without {\em HST} coverage.
The interpretation of the sample as a whole is not affected by the small number of galaxies without {\em HST} imaging.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}.}
\label{tab:phys-props}
\begin{tabular}{llllllllll}

@@

As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
For the galaxies without {\em HST} coverage, the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
This added an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.

\subsubsection{Position angles}\label{subsubsection:position_angle}
The second {\tt GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
We visually inspected each of the {\tt GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$ indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
We discuss this topic further in \cref{subsubsection:kin_and_phot}.
For the galaxies without {\em HST} coverage we fixed $PA_{morph}$ equal to $PA_{kin}$, for the analysis described in \cref{subsec:3d_modelling}.

@@

\subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
We aimed to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal-to-noise higher than both [O~{\sc III}]$\lambda$4959 and H$\beta$ and was detected over a larger area of each IFU. \\

@@

    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

\noindent
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\tt GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the typical $z\simeq3.0$ velocity dispersions, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
The reported errors on $\sigma_{int}$ take this assumption into account. \\

\noindent
The simulated intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
The velocity and velocity dispersion values were then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, seeking the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field:

@@

Following the construction of a convolved model cube and the measurement of the beam-smeared maps we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
We have re-evaluated the means and medians of the kinematic properties in these samples in order to make fair and reliable comparisons.
An overview of the comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.

@@

The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $57.0^{+6.6}_{-6.3}km\,s^{-1}$ respectively, which are less than observed for lower redshift typical star-forming galaxies (see \cref{subsec:results_rotation_vel} for a discussion).
In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
The magnitude of the beam-smearing correction ($V_{C}/V_{BS}$) has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}. \\

@@

By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion we recovered the beam-smearing correction for each galaxy.
The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50 km\,s$^{-1}$ i.e. $\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50 km\,s$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we did not attempt to fit the velocity dispersions, this is a feature the model could not reproduce.

To measure the $\sigma_{int}$ value for each galaxy in our sample we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{g,i}$ is the value in the ith spaxel recovered from the gaussian-fit.

@@

\noindent
The median of the $\sigma_{cor,i}$ map is taken as the $\sigma_{int}$ value for each galaxy and the median of the observed map is the $\sigma_{obs}$ value (see Table \ref{tab:kin_props}).
The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} km\,s^{-1}$ and $71.0^{+5.0}_{-4.8} km\,s^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
The magnitude of the beam-smearing correction ($\sigma_{int}/\sigma_{obs}$) has a mean and median value of 0.81 and 0.79 respectively for the isolated field sample. \\

>>>>

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\,\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal-to-noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\,\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a wealth of imaging and spectroscopic data.
Most of the galaxies for the KMOS observations had a confirmed spectroscopic redshift (see below).
A subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
In each pointing, few sources had no spectroscopic redshift and were selected on the basis of their photometric redshift.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).

@@

Two of the three field environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We selected targets from the various spectroscopic campaigns which have targeted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or $H\,\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
We name these GOODS-S-P1 and GOODS-S-P2, which which we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies quoted for GOODS-S-P2 does not include two observed targets which were later found to have $z < 0.5$.}

@@

To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\,\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, allowing both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however, due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

\subsubsection{Applying {\scriptsize GALFIT} to the imaging data}\label{subsubsec:galfitting}
We used {\scriptsize GALFIT} \citep{Peng2010_galfit} to fit 2D analytic functions, convolved with the PSF, to the observed {\em HST} images of the KDS field galaxies across GOODS-S and SSA22 in a consistent way.
The GOODS-S imaging data used is the latest release of the total field in {\it WFC3 F160W} band, which traces the rest-frame near-UV at $z\simeq3.5$, available via the CANDELS \citep{Grogin2011,Koekemoer2011} data access portal\footnote{\url{http://candels.ucolick.org/data_access/Latest_Release.html}}.
For SSA22 we made use of archival {\em HST} imaging\footnote{\url{https://archive.stsci.edu/hst/search.php}} data in the {\it WFC3 F160W} band (P.I. Lehmer: PID 13844; P.I. Mannucci: PID 11735) and the {\it ACS F814W} band, tracing $\simeq$ 2500$\AA$ light at $z\simeq3.1$ (P.I. Chapman: PID 10405; P.I. Abraham: PID 9760; P.I. Siana: PID 12527).
The {\em HST} coverage is shallower in SSA22 (exposure times of $\simeq5$ ks) and the {\it F160W} coverage is concentrated on the SSA22-cluster and so we resorted to the bluer {\it ACS F814W} data to derive morphological parameters in SSA22-P2 (also in SSA22-P2, 4 galaxies do not have any {\em HST} coverage as indicated in Table \ref{tab:phys-props}). \\

\noindent
We first ran SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\scriptsize GALFIT}, and then extracted postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we could not resolve more complicated morphological features such as spiral arms and bars and so we followed the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of $n=1$.
In the {\it F160W} band, the adopted PSF was a hybrid between the Tiny Tim {\it H}-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the {\it H}-band for the wings \citep{VanderWel2012} and in the {\it F814W} band we used the pure Tiny Tim {\it ACS} high-resolution PSF model.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, were free to vary.

@@

\noindent
This analysis provided us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
Example {\em HST} images and {\scriptsize GALFIT} outputs are given in Figure \ref{fig:main_body_kinematic_grids} for selected galaxies, and maps for the full isolated field sample (see \cref{subsubsection:spaxel_fitting}) are plotted throughout Appendix \ref{app:kinematics_plots}.

The errorbars produced by {\scriptsize GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
In each of the following sections we also discuss the approach followed to recover the morphological parameters for the galaxies without {\em HST} coverage.
The interpretation of the sample as a whole is not affected by the small number of galaxies without {\em HST} imaging.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\scriptsize GALFIT} \protect\citep{Peng2010_galfit}.}
\label{tab:phys-props}
\begin{tabular}{llllllllll}

@@

As mentioned in \cref{subsubsec:galfitting}, the error reported by {\scriptsize GALFIT} on the model $b/a$ value is unrealistically small.
Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
For the galaxies without {\em HST} coverage, the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
This added an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.

\subsubsection{Position angles}\label{subsubsection:position_angle}
The second {\scriptsize GALFIT} parameter was $PA_{morph}$, which is the direction of the photometric major axis of the galaxy on the sky.
We visually inspected each of the {\scriptsize GALFIT} maps to check that the derived $PA_{morph}$ follows the galaxy light distribution (with $PA_{morph}$ indicated by the orange dashed line in Figure \ref{fig:main_body_kinematic_grids}) and when this was not the case it was usually an indication of multiple distinct components or tidal streams (see \cref{subsec:morpho-kin-class} where we remove multiple-component objects from the final sample).
We note that discrepancy between $PA_{morph}$ and the kinematic position angle, $PA_{kin}$, is an indicator of sub-structure in the morphology \citep[e.g.][]{Queyrel2012,Wisnioski2015,Rodrigues2017}, and deviations can indicate clumps or mergers which may influence the underlying kinematics or bias the derived $PA_{morph}$ towards a particular direction.
We discuss this topic further in \cref{subsubsection:kin_and_phot}.
For the galaxies without {\em HST} coverage we fixed $PA_{morph}$ equal to $PA_{kin}$, for the analysis described in \cref{subsec:3d_modelling}.

@@

\subsubsection{Spaxel Fitting}\label{subsubsection:spaxel_fitting}
We aimed to extract two-dimensional maps of the [O~{\sc III}]$\lambda$5007 flux, velocity and velocity dispersion from each of the 62 stacked and calibrated KDS datacubes with an [O~{\sc III}]$\lambda$5007 detection.
These properties are extracted via modelling emission line profiles within each spaxel, with a set of acceptance criteria imposed to determine whether the fit quality is high enough to allow the inferred properties to pass into the final 2D maps of the flux and kinematics.
We concentrated solely on the [O~{\sc III}]$\lambda$5007 emission line which always had signal-to-noise higher than both [O~{\sc III}]$\lambda$4959 and $H\,\beta$ and was detected over a larger area of each IFU. \\

@@

    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
    For each galaxy we plot on the top row the {\em HST} image, {\scriptsize GALFIT} model and {\scriptsize GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\scriptsize GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

\noindent
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction was determined using the {\scriptsize GALFIT} model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile) and the intrinsic velocity dispersion of the line was set to follow a uniform distribution with a default width of 50 km\,s$^{-1}$.
This default line width was selected following examination of figure 10 of \cite{Wisnioski2015}, which places observational constraints on the velocity dispersions of typical star-forming galaxies at $z\simeq3.0$, and we discuss the impact of this assumption in Appendix \ref{appsubsec:model_errors} by using sensible alternative values.
The reported errors on $\sigma_{int}$ take this assumption into account. \\

\noindent
The simulated, intrinsic [O~{\sc III}]$\lambda$5007 cube was then convolved slice by slice using fast Fourier transform libraries with the {\it K}-band atmospheric seeing profile (Table \ref{tab:pointings}).
The velocity and velocity dispersion values were then re-measured in each spaxel to produce `beam-smeared' 2D maps of the kinematic parameters.
We fit the beam-smeared velocity field to the observed velocity field, using MCMC sampling with the python package `emcee' \citep{Foreman-Mackey2013} to vary the intrinsic model parameters, seeking the combination of parameters which maximises the log-Likelihood function given by Equation \ref{eq:likelihood}, which fully accounts for the errors on the observed velocity field:

@@

Following the construction of a convolved model cube and the measurement of the beam-smeared maps, we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
We have re-evaluated the means and medians of the kinematic properties in these samples in order to make fair and reliable comparisons.
An overview of the comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.

@@

The mean and median $V_{C}$ values for the isolated field sample are $76.7^{+4.9}_{-4.5}km\,s^{-1}$ and $57.0^{+6.6}_{-6.3}km\,s^{-1}$ respectively, which are less than observed for lower redshift typical star-forming galaxies (see \cref{subsec:results_rotation_vel} for a discussion).
In order to determine the beam-smearing correction factor, we also extracted the velocity from the beam-smeared model at the convolved $2R_{1/2}$ radius, represented by the vertical blue dashed line in Figure \ref{fig:main_body_kinematic_grids}, to recover the beam-smeared velocity, $V_{BS}$.
The magnitude of the beam-smearing correction, ($V_{C}/V_{BS}$), has a mean and median value of 1.29 and 1.21 for the isolated field sample and we discuss the observational and model uncertainties which combine to give the $V_{C}$ errors in Appendix \ref{appsubsec:model_errors}. \\

@@

By comparing the best-fitting simulated datacube with the assumption for the isotropic velocity dispersion, we recovered the beam-smearing correction for each galaxy.
The 2D beam-smearing correction map, $\sigma_{BS}$, was computed on a spaxel-by-spaxel basis as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion of 50 km\,s$^{-1}$ i.e. $\sigma_{BS,i} = \sigma_{simulated,i} - \sigma_{assumed,i}$ (where $\sigma_{assumed,i}$ was fixed at 50 km\,s$^{-1}$ as described in \cref{subsubec:model_cube} and $\sigma_{simulated,i}$ is the simulated velocity dispersion recovered under this assumption).
The impact of the value of $\sigma_{assumed}$ on the magnitude of the $\sigma_{BS,i}$ correction is discussed further in Appendix \ref{appsubsec:model_errors} and the $\sigma_{int}$ errors take this into account.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we did not attempt to fit the velocity dispersions, this is a feature the model could not reproduce.

To measure the $\sigma_{int}$ value for each galaxy in our sample, we applied Equation \ref{eq:owen_sigma} in each spaxel to derive an intrinsic sigma map, where $\sigma_{g,i}$ is the value in the ith spaxel recovered from the gaussian-fit to the [O~{\sc III}]$\lambda$5007 emission line.

@@

\noindent
The median of the $\sigma_{cor,i}$ map is taken as the $\sigma_{int}$ value for each galaxy and the median of the observed map is the $\sigma_{obs}$ value (see Table \ref{tab:kin_props}).
The mean and median $\sigma_{int}$ values in the isolated field sample are $70.8^{+3.3}_{-3.1} km\,s^{-1}$ and $71.0^{+5.0}_{-4.8} km\,s^{-1}$ respectively, higher than for typical star-forming galaxies at lower redshift as has been extensively reported \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
The magnitude of the beam-smearing correction, ($\sigma_{int}/\sigma_{obs}$), has a mean and median value of 0.81 and 0.79 respectively for the isolated field sample. \\
